---
title: "Back up"
author: "Benjamin Nicklas"
date: "2025-05-28"
output: html_document
---

```{r}
#Reads table, by indicating path to directory where the dataset is stored, and stores it to variable NS_Table (NS for Non-synchronizied HeLa-cells)

NS_Table <- read.table("Daten/Daten_Kommata_behoben.csv", header=TRUE, row.names=1, sep = ";")
```

```{r}
levels_CR <- factor(rep(c("CTRL", "RNASE"),75))
```

```{r}
levels_fraction <- factor(rep(c("Ctrl_Rep1","RNase_Rep1","Ctrl_Rep2","RNase_Rep2","Ctrl_Rep3","RNase_Rep3"),25))
```

```{r}
fraction_names <- as.vector(matrix(rep(paste("fraction",1:25,sep=""),6), nrow = 6, ncol=25, byrow = TRUE))
```

```{r}
# The number of rows are stored in a variable
n_row <- nrow(NS_Table)

# The row names (protein names) are stored in a variable
row_names <- rownames(NS_Table)
```

```{r}
colmns_sorted <- data.frame(row.names = colnames(NS_Table), levels_CR = levels_CR, levels_fraction = levels_fraction, fraction_names = fraction_names)
```


```{r}

fraction.tables <- lapply(paste("fraction", 1:25, sep = ""), function(fx) {NS_Table[, colmns_sorted$fraction == fx]})

names(fraction.tables) <- paste("fraction", 1:25, sep = "")

selected_proteins <- names(fraction.tables)
```


```{r}
# Liste mit nur CTRL-Spalten für jede Fraktion
fraction.tables.CTRL <- lapply(selected_proteins, function(fx) {
  cols <- rownames(subset(colmns_sorted, fraction_names == fx & levels_CR == "CTRL")) 
  NS_Table[, cols, drop = FALSE]
  })

# Liste mit nur RNASE-Spalten für jede Fraktion
fraction.tables.RNASE <- lapply(selected_proteins, function(fx) {
  cols <- rownames(subset(colmns_sorted, fraction_names == fx & levels_CR == "RNASE"))
  NS_Table[, cols, drop = FALSE]})

names(fraction.tables.CTRL) <- selected_proteins
names(fraction.tables.RNASE) <- selected_proteins
```

```{r}
avg.tables.CTRL <- lapply(fraction.tables.CTRL, function(df) {
  sapply(df, mean)
})

avg.tables.RNASE <- lapply(fraction.tables.RNASE, function(df) {
  sapply(df, mean)
})

avg.tables.CTRL[["fraction1"]]
avg.tables.RNASE[["fraction1"]]
```


```{r}
norm_fact <- function(x) {
				if( (abs(x[1]-x[2])<abs(x[1]-x[3])) && (abs(x[1]-x[2])<abs(x[2]-x[3])) ) 
					{mean(c(x[1],x[2]))} else if( (abs(x[1]-x[3])<abs(x[1]-x[2])) && (abs(x[1]-x[3])<abs(x[2]-x[3])) )
												  {mean(c(x[1],x[3]))} else {mean(c(x[2],x[3]))} 
}

print(norm_fact(avg.tables.CTRL[["fraction1"]]))

```


```{r}
norm_mean_frxn_CTRL <- lapply(avg.tables.CTRL, function(vec) {
  norm_factor <- norm_fact(vec)
  norm_factor / vec 
})

norm_mean_frxn_RNASE <- lapply(avg.tables.RNASE, function(vec) {
  norm_factor <- norm_fact(vec)
  norm_factor / vec 
})

print(norm_mean_frxn_CTRL[[1]])
```
```{r}
# Normierungsvektoren für CTRL, Replikat 1–3
norm.ctrl1 <- sapply(norm_mean_frxn_CTRL, function(x) x[1])
norm.ctrl2 <- sapply(norm_mean_frxn_CTRL, function(x) x[2])
norm.ctrl3 <- sapply(norm_mean_frxn_CTRL, function(x) x[3])

# Und genauso für RNASE
norm.rnase1 <- sapply(norm_mean_frxn_RNASE, function(x) x[1])
norm.rnase2 <- sapply(norm_mean_frxn_RNASE, function(x) x[2])
norm.rnase3 <- sapply(norm_mean_frxn_RNASE, function(x) x[3])
```


```{r}
data.ctrl1 <- colmns_sorted$levels_fraction =="Ctrl_Rep1"
data.ctrl2 <- colmns_sorted$levels_fraction =="Ctrl_Rep2"
data.ctrl3 <- colmns_sorted$levels_fraction =="Ctrl_Rep3"
data.rnase1 <- colmns_sorted$levels_fraction =="RNase_Rep1"
data.rnase2 <- colmns_sorted$levels_fraction =="RNase_Rep2"
data.rnase3 <- colmns_sorted$levels_fraction =="RNase_Rep3"

```


```{r}
# Hilfsfunktion: multipliziert Spalten von NS_Table mit den jeweiligen Normfaktoren
normalize_group <- function(mask, norm_vec) {
  selected <- NS_Table[, mask]                  # Spalten für die jeweilige Gruppe
  as.data.frame(mapply(`*`, selected, norm_vec, SIMPLIFY = FALSE))  # Elementweise Multiplikation
}

# Anwendung auf alle Gruppen
table.ctrl1  <- normalize_group(data.ctrl1,  norm.ctrl1)
table.ctrl2  <- normalize_group(data.ctrl2,  norm.ctrl2)
table.ctrl3  <- normalize_group(data.ctrl3,  norm.ctrl3)
table.rnase1 <- normalize_group(data.rnase1, norm.rnase1)
table.rnase2 <- normalize_group(data.rnase2, norm.rnase2)
table.rnase3 <- normalize_group(data.rnase3, norm.rnase3)
```

```{r}
rownames(table.ctrl1) <- row_names
rownames(table.ctrl2) <- row_names
rownames(table.ctrl3) <- row_names
rownames(table.rnase1) <- row_names
rownames(table.rnase2) <- row_names
rownames(table.rnase3) <- row_names
```

```{r}
smooth_table <- function(tbl) {
  data.frame(tbl[1], (tbl[1:23] + tbl[2:24] + tbl[3:25]) / 3, tbl[25])
}

table.ctrl1.SW <- smooth_table(table.ctrl1)
table.ctrl2.SW <- smooth_table(table.ctrl2)
table.ctrl3.SW <- smooth_table(table.ctrl3)
table.rnase1.SW <- smooth_table(table.rnase1)
table.rnase2.SW <- smooth_table(table.rnase2)
table.rnase3.SW <- smooth_table(table.rnase3)
```

```{r}
# Get the proper rownames for the tables
colnames(table.ctrl1.SW) <- colnames(table.ctrl1)
colnames(table.ctrl2.SW) <- colnames(table.ctrl2)
colnames(table.ctrl3.SW) <- colnames(table.ctrl3)
colnames(table.rnase1.SW) <- colnames(table.rnase1)
colnames(table.rnase2.SW) <- colnames(table.rnase2)
colnames(table.rnase3.SW) <- colnames(table.rnase3)
```

```{r}
# Funktion zur Zeilennormalisierung (auf 100 %)
normalize_table <- function(tbl) {
  tbl * 100 / rowSums(tbl)
}


tables.ctrl <- list(
  ctrl1 = table.ctrl1.SW,
  ctrl2 = table.ctrl2.SW,
  ctrl3 = table.ctrl3.SW)

tables.rnase <- list(
  rnase1 = table.rnase1.SW,
  rnase2 = table.rnase2.SW,
  rnase3 = table.rnase3.SW)

norm_tables.ctrl <- lapply(tables.ctrl, normalize_table)
norm_tables.rnase <- lapply(tables.rnase, normalize_table)

norm_tables.rnase$rnase1
```
```{r}
# Funktion zum Ersetzen von NA und NaN durch 0
clean_table <- function(tbl) {
  tbl <- rapply(tbl, function(x) ifelse(is.na(x), 0, x), how = "replace")
  tbl <- rapply(tbl, function(x) ifelse(is.nan(x), 0, x), how = "replace")
  return(tbl)
}

# Liste der Tabellen
tables.norm.ctrl <- list(
  ctrl1 = table.ctrl1.SW.norm,
  ctrl2 = table.ctrl2.SW.norm,
  ctrl3 = table.ctrl3.SW.norm)

tables.norm.rnase <- list(
  rnase1 = table.rnase1.SW.norm,
  rnase2 = table.rnase2.SW.norm,
  rnase3 = table.rnase3.SW.norm)

# Bereinigen
tables.norm.ctrl <- lapply(tables.norm.ctrl, clean_table)
tables.norm.rnase <- lapply(tables.norm.rnase, clean_table)

View(tables.norm.ctrl$ctrl1)

```

```{r}
# Average value for normalization of CTRL and RNASE samples to 100
my.list.ctrl.norm <- list(table.ctrl1.SW, table.ctrl2.SW, table.ctrl3.SW)
my.list.rnase.norm <- list(table.rnase1.SW, table.rnase2.SW, table.rnase3.SW)

ctrl_norm_mean <- Reduce("+", my.list.ctrl.norm)/length(my.list.ctrl.norm)
rnase_norm_mean <- Reduce("+", my.list.rnase.norm)/length(my.list.rnase.norm)

```

```{r}
# Change names of the columns: from "fraction1" to "fraction25"
col_fractions <- paste("fraction",1:25,sep="")
colnames(ctrl_norm_mean) <- col_fractions
colnames(rnase_norm_mean) <- col_fractions
```

```{r}
# Normalization to 100 for each protein (= the sum of the amount of protein from fraction1 to fraction25 is 100)
ctrl_norm_mean <- ctrl_norm_mean*100/rowSums(ctrl_norm_mean)
rnase_norm_mean <- rnase_norm_mean*100/rowSums(rnase_norm_mean)

```

```{r}
replace_na_nan <- function(x) rapply(x, function(y) ifelse(is.na(y) | is.nan(y), 0, y), how = "replace")

ctrl_norm_mean <- replace_na_nan(ctrl_norm_mean)
rnase_norm_mean <- replace_na_nan(rnase_norm_mean)
```

```{r}
ctrl_norm_mean[rowSums(rnase_norm_mean[1:25])==0,] <- 0
rnase_norm_mean[rowSums(ctrl_norm_mean[1:25])==0,] <- 0

View(ctrl_norm_mean)
```





```{r}
#Nicht wirklich teil des Codes nur falls ich das nochmal brauche
fraction.tables0 <- lapply(fraction.tables, function(subtable) {subtable[rowSums(subtable != 0) > 0, ]})

selected_proteins <- names(fraction.tables0)

View(fraction.tables0[[1]])
View(fraction.tables[[1]])

names(fraction.tables) <- paste("fraction", 1:25, sep = "")

selected_proteins <- names(fraction.tables)
```

---
title: "Data set"
author: "Julia Annika Ferdin"
date: "2025-05-04"
output: html_document
---
**************************************************************************************************************
Mass spectrometry analysis of non-synchronized HeLa cells
**************************************************************************************************************

Script is divided into different parts:
1 - Read dataset, normalization between replicated, sliding window?, normalization to sum = 100
2 - Find local maxima greater than 2 as fit parameters
3 - Gaussian fit on each curve (per protein, three control and three Rnase replicates)
4 - Quality control of fit an if possible adjustment
5 - Asses p-values and FDR-adjusted p-values for each maximum
6 - Evaluate shifts by using selection criteria
7 - Compute final table and export as csv file
Graphics 1 - Average curves for one protein of interest - function curves_plot
Graphics 2 - All curves for one protein of interest- function curves_all


**************************************************************************************************************
1 - Read dataset, normalization between replicated, sliding window?, normalization to sum = 100
**************************************************************************************************************

```{r}
#Reads table, by indicating path to directory where the dataset is stored, and stores it to variable NS_Table (NS for Non-synchronizied HeLa-cells)

NS_Table <- read.table("Daten/Daten_Kommata_behoben.csv", header=TRUE, row.names=1, sep = ";")
```

```{r}
#The first 12 titles of the table (NS_Table) rows/colums are read out

#Row names are protein names
head(rownames(NS_Table),12)

#Columns indicate the respective fractions from 1 to 25, and their replicated
head(colnames(NS_Table),12)
```

**************************************************************************************************************
Rearrange and reorder the columns to their fraction and treatment to simplify the following work steps. 

Creating 3 vectors that describe the characteristics of the columns (i.e., samples) in the data set:
levels_CR → indicates whether the sample was treated with RNASE or as a CTRL
levels_fraction → labels the column with the replicate number (1–3) for either CTRL or RNASE
fraction_names → creates the variables fraction1 to fraction25 to assign the replicates to each fraction

```{r}
#A vector consists of 2 variables (CTRL, RNASE) --> c("CTRL", "RNASE")
#The factor() function encodes a vector as a factor. The 2 variables CTRL and RNASE are ordered into 2 different levels (characters)
#rep(vector,75) repeats the factor() function 75 times, because we have 150 columns (75 times CTRL and RNASE)
#The factor is defined as the variable 'treatment'

levels_CR <- factor(rep(c("CTRL", "RNASE"),75))
```

```{r}
#Every sample of every fraction gets its own level to disconnect them from each other -> 6 levels per fraction because we have 3 CTRLs and 3 RNASEs per fraction

levels_fraction <- factor(rep(c("Ctrl_Rep1","RNase_Rep1","Ctrl_Rep2","RNase_Rep2","Ctrl_Rep3","RNase_Rep3"),25))
View(levels_fraction)
```

```{r}
# Creation of a matrix with 6 rows and 25 columns. The matrix is filled by row from fraction1 to fraction25 so every column has one single fraction.
# sep="" compares the word fraction with the numbers 1 to 25 without a blank space.
# paste("fraction",1:25,sep="") creates a vector with the strings fraction1 to fraction25
# as.vector changes the created matrix into a vector with 150 elements sorted from 6 times fraction1 to 6 times fraction25

fraction_names <- as.vector(matrix(rep(paste("fraction",1:25,sep=""),6), nrow = 6, ncol=25, byrow = TRUE))

View(matrix(rep(paste("fraction",1:25,sep=""),6), nrow = 6, ncol=25, byrow = TRUE))
```

```{r}
# The number of rows are stored in a variable
n_row <- nrow(NS_Table)

# The row names (protein names) are stored in a variable
row_names <- rownames(NS_Table)
```

```{r}
# Creation of a data frame with levels_CR, levels_fraction and fraction_names. This assigns every replicate of the factions (levels_fraction) to their fraction (fraction_names) and their kind of treatment, CRTL or RNASE (levels_CR).

colmns_sorted <- data.frame(row.names = colnames(NS_Table), levels_CR = levels_CR, levels_fraction = levels_fraction, fraction_names = fraction_names)

View(colmns_sorted)

#Check for missing values, there are none 
anyNA(NS_Table)
```


**************************************************************************************************************
Normalization step between the replicates in each fraction and for each treatment using the mean value method

```{r}
# lapply executes for every with paste  created string (the fractions) a function fx
# colmns_sorted$fraction == fx: checks which columns are part of the fractions fx
# NS_Table[, ...] filters just these columns and assigns them to the list "fraction.tables"
# names(fraction.tables): the list "fraction.tables" gets names for its segments and assigns them to the variable selected_proteins 

fraction.tables <- lapply(paste("fraction", 1:25, sep = ""), function(fx) {NS_Table[, colmns_sorted$fraction == fx]})

names(fraction.tables) <- paste("fraction", 1:25, sep = "")

selected_proteins <- names(fraction.tables)
```


```{r}
# List with just CTRL/RNASE columns for each fraction
# subset filters just the fractions that fulfill the conditions: fraction_names == fx --> fraction name is part of the funtion fx, levels_CR == "CTRL" --> protein was treated as a CTRL
# rownames() takes the rownames of the filtert fractions and asigns them to the variable col
# NS_Table[, cols, drop = FALSE] the names that are part of NS_Table are filterd out and drop = FALSE makes sure that fraction.tables.CTRL will be a dataframe

# Liste mit nur CTRL-Spalten für jede Fraktion
fraction.tables.CTRL <- lapply(selected_proteins, function(fx) {
  cols <- rownames(subset(colmns_sorted, fraction_names == fx & levels_CR == "CTRL")) 
  NS_Table[, cols, drop = FALSE]
  })

# Liste mit nur RNASE-Spalten für jede Fraktion
fraction.tables.RNASE <- lapply(selected_proteins, function(fx) {
  cols <- rownames(subset(colmns_sorted, fraction_names == fx & levels_CR == "RNASE"))
  NS_Table[, cols, drop = FALSE]})

names(fraction.tables.CTRL) <- selected_proteins
names(fraction.tables.RNASE) <- selected_proteins

View(fraction.tables.CTRL[["fraction3"]])
```

```{r}
# sapply(df, mean) calculates the mean of every column of the dataframe fraction.tables.CTRL

avg.tables.CTRL <- lapply(fraction.tables.CTRL, function(df) {
  sapply(df, mean)
})

avg.tables.RNASE <- lapply(fraction.tables.RNASE, function(df) {
  sapply(df, mean)
})

avg.tables.CTRL[["fraction1"]]
avg.tables.RNASE[["fraction1"]]
```
```{r}
#--> prinzpiell wird mit diesem Code gesagt, dass mindestens 1 Wert immer ein Messfehler sein muss, müssen wir uns überlegen, ob wir das genauso machen wollen oder ob wir alle 3 Messwerte mit einbeziehen.
# Determine normalization factor for each condition (i.e. sample), as the mean of the 2 most similar replicates.
# Create a function norm_fact for this step:

norm_fact <- function(x) {
				if( (abs(x[1]-x[2])<abs(x[1]-x[3])) && (abs(x[1]-x[2])<abs(x[2]-x[3])) ) 
					{mean(c(x[1],x[2]))} else if( (abs(x[1]-x[3])<abs(x[1]-x[2])) && (abs(x[1]-x[3])<abs(x[2]-x[3])) )
												  {mean(c(x[1],x[3]))} else {mean(c(x[2],x[3]))} 
}


print(norm_fact(avg.tables.CTRL[["fraction1"]]))
```

```{r}
# normalization of the mean value vectors - inversely proportional to the size of the values
# norm_factor / vec: gives a new vector indicating how strong each element is relative to the norm factor (mean)

norm_mean_frxn_CTRL <- lapply(avg.tables.CTRL, function(vec) {
  norm_factor <- norm_fact(vec)
  norm_factor / vec 
})

norm_mean_frxn_RNASE <- lapply(avg.tables.RNASE, function(vec) {
  norm_factor <- norm_fact(vec)
  norm_factor / vec 
})

print(norm_mean_frxn_CTRL[[1]])
```


```{r}
# Correction factor for the overall protein quantity
# Normalization vectors for replicates 1-3
# function(x) x[1]: extracts the first element of each vector in the list
# norm.ctrl1 is a numeric vector consisting of the 1st element of each normalized CTRL vector

norm.ctrl1 <- sapply(norm_mean_frxn_CTRL, function(x) x[1])
norm.ctrl2 <- sapply(norm_mean_frxn_CTRL, function(x) x[2])
norm.ctrl3 <- sapply(norm_mean_frxn_CTRL, function(x) x[3])

norm.rnase1 <- sapply(norm_mean_frxn_RNASE, function(x) x[1])
norm.rnase2 <- sapply(norm_mean_frxn_RNASE, function(x) x[2])
norm.rnase3 <- sapply(norm_mean_frxn_RNASE, function(x) x[3])
```

```{r}
# Defines logical vectors (TRUE, FALSE), which are later used to create subtables - separately for treatment (Ctrl vs. RNase) and replica (Rep1, Rep2, Rep3)
# colmns_sorted$levels_fraction =="Ctrl_Rep1": checks at which position exactly in the columns_sorted Ctrl_Rep1 can be found (marks it with TRUE)

data.ctrl1 <- colmns_sorted$levels_fraction =="Ctrl_Rep1"
data.ctrl2 <- colmns_sorted$levels_fraction =="Ctrl_Rep2"
data.ctrl3 <- colmns_sorted$levels_fraction =="Ctrl_Rep3"
data.rnase1 <- colmns_sorted$levels_fraction =="RNase_Rep1"
data.rnase2 <- colmns_sorted$levels_fraction =="RNase_Rep2"
data.rnase3 <- colmns_sorted$levels_fraction =="RNase_Rep3"
```

**************************************************************************************************************
```{r}
# Normalization step, fraction-wise
# takes specific columns from the protein intensity table and scales each row according to a normalization factor to compensate for measurement differences between replicates
# mask: A logical vector (TRUE/FALSE) that specifies which columns of NS_Table are selected
# selected <- NS_Table[, mask]: from NS_Table only the columns marked with TRUE in mask are selected
# (`*`, selected, norm_vec, SIMPLIFY = FALSE): Multiplication of colums of selected and the vector norm_vec saved as a list

normalize_group <- function(mask, norm_vec) {
  selected <- NS_Table[, mask]                  
  as.data.frame(mapply(`*`, selected, norm_vec, SIMPLIFY = FALSE))
}

# logical vectors (data.ctrl1) and vectors with normalization-factors (norm.ctrl1) form groups
# normalize_group(): multiplication of the vectors with their normalization-factor

table.ctrl1  <- normalize_group(data.ctrl1,  norm.ctrl1)
table.ctrl2  <- normalize_group(data.ctrl2,  norm.ctrl2)
table.ctrl3  <- normalize_group(data.ctrl3,  norm.ctrl3)
table.rnase1 <- normalize_group(data.rnase1, norm.rnase1)
table.rnase2 <- normalize_group(data.rnase2, norm.rnase2)
table.rnase3 <- normalize_group(data.rnase3, norm.rnase3)

```

```{r}
# Get the proper rownames for the tables

rownames(table.ctrl1) <- row_names
rownames(table.ctrl2) <- row_names
rownames(table.ctrl3) <- row_names
rownames(table.rnase1) <- row_names
rownames(table.rnase2) <- row_names
rownames(table.rnase3) <- row_names

View(table.ctrl1)
```

**************************************************************************************************************
```{r}
# Apply a sliding window/moving average of 3 points to the data to reduce noise in the data and obtain smoother curves (not possible for fraction 1 and 25)

smooth_table <- function(tbl) {
  data.frame(tbl[1], (tbl[1:23] + tbl[2:24] + tbl[3:25]) / 3, tbl[25])
}

table.ctrl1.SW <- smooth_table(table.ctrl1)
table.ctrl2.SW <- smooth_table(table.ctrl2)
table.ctrl3.SW <- smooth_table(table.ctrl3)
table.rnase1.SW <- smooth_table(table.rnase1)
table.rnase2.SW <- smooth_table(table.rnase2)
table.rnase3.SW <- smooth_table(table.rnase3)
```

```{r}
# Get the proper rownames for the tables

colnames(table.ctrl1.SW) <- colnames(table.ctrl1)
colnames(table.ctrl2.SW) <- colnames(table.ctrl2)
colnames(table.ctrl3.SW) <- colnames(table.ctrl3)
colnames(table.rnase1.SW) <- colnames(table.rnase1)
colnames(table.rnase2.SW) <- colnames(table.rnase2)
colnames(table.rnase3.SW) <- colnames(table.rnase3)

View(table.ctrl1.SW)
```

**************************************************************************************************************
```{r}
# Normalization of the fractions: Sum of all fraction values equals 100 (%)

normalize_table <- function(tbl) {
  tbl * 100 / rowSums(tbl)
}


tables.ctrl <- list(
  ctrl1 = table.ctrl1.SW,
  ctrl2 = table.ctrl2.SW,
  ctrl3 = table.ctrl3.SW)

tables.rnase <- list(
  rnase1 = table.rnase1.SW,
  rnase2 = table.rnase2.SW,
  rnase3 = table.rnase3.SW)

# Calculation of the percentages of the fractions in the normalized table (table.ctrl1.SW)

norm_tables.ctrl <- lapply(tables.ctrl, normalize_table)
norm_tables.rnase <- lapply(tables.rnase, normalize_table)

norm_tables.rnase$rnase1
```

**************************************************************************************************************
```{r}
# Function for replacing NA and NaN with 0

clean_table <- function(tbl) {
  tbl <- rapply(tbl, function(x) ifelse(is.na(x), 0, x), how = "replace")
  tbl <- rapply(tbl, function(x) ifelse(is.nan(x), 0, x), how = "replace")
  return(tbl)
}

tables.norm.ctrl <- list(
  ctrl1 = table.ctrl1.SW.norm,
  ctrl2 = table.ctrl2.SW.norm,
  ctrl3 = table.ctrl3.SW.norm)

tables.norm.rnase <- list(
  rnase1 = table.rnase1.SW.norm,
  rnase2 = table.rnase2.SW.norm,
  rnase3 = table.rnase3.SW.norm)

# Getting the clean table

tables.norm.ctrl <- lapply(tables.norm.ctrl, clean_table)
tables.norm.rnase <- lapply(tables.norm.rnase, clean_table)

View(tables.norm.ctrl$ctrl1)

```

**************************************************************************************************************
```{r}
my.list.ctrl.norm <- list(table.ctrl1.SW, table.ctrl2.SW, table.ctrl3.SW)
my.list.rnase.norm <- list(table.rnase1.SW, table.rnase2.SW, table.rnase3.SW)

# Addition of all data-frames in the list my.list.ctrl.norm (element-wise) and Division of the Sum with 3 to get the mean of all 3 replicates

ctrl_norm_mean <- Reduce("+", my.list.ctrl.norm)/length(my.list.ctrl.norm)
rnase_norm_mean <- Reduce("+", my.list.rnase.norm)/length(my.list.rnase.norm)
```

```{r}
# Change names of the columns: from "fraction1" to "fraction25"

col_fractions <- paste("fraction",1:25,sep="")
colnames(ctrl_norm_mean) <- col_fractions
colnames(rnase_norm_mean) <- col_fractions
```

```{r}
# second normalization of the fractions (mean destroyed first normalization): Sum of all fraction values equals 100 (%)

ctrl_norm_mean <- ctrl_norm_mean*100/rowSums(ctrl_norm_mean)
rnase_norm_mean <- rnase_norm_mean*100/rowSums(rnase_norm_mean)

```

```{r}
# Function for replacing NA and NaN with 0

replace_na_nan <- function(x) rapply(x, function(y) ifelse(is.na(y) | is.nan(y), 0, y), how = "replace")

ctrl_norm_mean <- replace_na_nan(ctrl_norm_mean)
rnase_norm_mean <- replace_na_nan(rnase_norm_mean)
```

```{r}
# If a curve is 0 in all fractions, the other fraction is also set to 0 and is excluded from the analysis

ctrl_norm_mean[rowSums(rnase_norm_mean[1:25])==0,] <- 0
rnase_norm_mean[rowSums(ctrl_norm_mean[1:25])==0,] <- 0

View(ctrl_norm_mean)
View(rnase_norm_mean)
```

Weiter hab ich noch nicht den Code bearbeitet 
LG Ben
