---
title: "Data set"
author: "Julia Annika Ferdin"
date: "2025-05-04"
output: html_document
---
**************************************************************************************************************
Mass spectrometry analysis of non-synchronized HeLa cells
**************************************************************************************************************

Script is divided into different parts:
1 - Read dataset, normalization between replicated, sliding window?, normalization to sum = 100
2 - Find local maxima greater than 2 as fit parameters
3 - Gaussian fit on each curve (per protein, three control and three Rnase replicates)
4 - Quality control of fit an if possible adjustment
5 - Asses p-values and FDR-adjusted p-values for each maximum
6 - Evaluate shifts by using selection criteria
7 - Compute final table and export as csv file
Graphics 1 - Average curves for one protein of interest - function curves_plot
Graphics 2 - All curves for one protein of interest- function curves_all


**************************************************************************************************************
1 - Read dataset, normalization between replicated, sliding window?, normalization to sum = 100
**************************************************************************************************************

Do we need this chunk?
Wird das überhaupt noch gebraucht, ich denke eigentlich kann das weg.
```{r}
#Checks, if dataset is stored on local directory
file.exists("C:/Users/julia/Documents/2025-topic-03-group-01/Daten/Daten.csv")
```



```{r}
#Reads table, by indicating path to directory where the dataset is stored, and stores it to variable NS_Table (NS for Non-synchronizied)
NS_Table <- read.table("Daten/Daten_Kommata_behoben.csv", header=TRUE, row.names=1, sep = ";")
```

```{r}
#Row names are protein names
head(rownames(NS_Table),12)

#Columns indicate the respective fractions from 1 to 25, and their replicated
head(colnames(NS_Table),12)
```

Why do we need this chunk? 
```{r,results='hide'}
#Give teammates ability to view data set
#read.csv("Daten/Daten.csv")
#NS_Table <- read.csv("Daten/Daten.csv", header=TRUE, row.names=1, sep = ";")
View(NS_Table)
```

**************************************************************************************************************
Define the information found in table

Creating 3 vectors that describe the characteristics of the columns (i.e., samples) in the dataset:
treatment → indicates whether the sample in the column is a control (CTRL) or rnase (RNASE) replicate
condition → labels the column with the replicate number (1–3) for either CTRL or RNASE
fraction → indicates which fraction the sample belongs to

```{r}
# Use factors to define the treatment in the samples as control (CTRL) or rnase (RNASE) - there are as many treatments as columns in the table. Here, we have 150 treatments
#factor() encodes a vector as a factor. Can be used to order different levels, here we have the two levels CTRL and RNASE
#rep() replicates the values in x
treatment <- factor(rep(c("CTRL", "RNASE"),75))
```

```{r}
# Use factors to define the condition in the samples. Here we have all six replicates for 1 fraction after each other and then the next fractions.
condition <- factor(rep(c("Ctrl_Rep1","RNase_Rep1","Ctrl_Rep2","RNase_Rep2","Ctrl_Rep3","RNase_Rep3"),25))
```

```{r}
# Use factors to define the fractions from fraction1 to fraction25 through the 150 columns. Here, we have first all six fraction1, then all six fraction2 etc ... until all six fraction25
fraction <- as.vector(matrix(rep(paste("fraction",1:25,sep=""),6), nrow = 6, ncol=25, byrow = TRUE))
```

```{r}
# Store the number of rows in a variable
n_row <- nrow(NS_Table)

# Store the row names (here the name sof the proteins) in a variable
row_names <- rownames(NS_Table)
```

```{r}
# Make dataframe with the information (treatment, condition, fraction) for each column - here 150 columns
data <- data.frame(row.names = colnames(NS_Table), treatment = treatment, condition = condition, fraction = fraction)

#Check for missing values, there are none 
anyNA(NS_Table)
```


**************************************************************************************************************
Normalization step between the replicates in each fraction and for each treatment using the mean value method


```{r}
# Define one new table per fraction containing the 3 CTRL and 3 RNASE replicates.

# CODE: NS_Table[,data$fraction =="fraction1"] extracts each protein as a row from NS_Table, but only includes the columns of samples that have the factor "fraction_" with the corresponding fraction number.
table.frxn1 <- NS_Table[,data$fraction =="fraction1"]
table.frxn2 <- NS_Table[,data$fraction =="fraction2"]
table.frxn3 <- NS_Table[,data$fraction =="fraction3"]
table.frxn4 <- NS_Table[,data$fraction =="fraction4"]
table.frxn5 <- NS_Table[,data$fraction =="fraction5"]
table.frxn6 <- NS_Table[,data$fraction =="fraction6"]
table.frxn7 <- NS_Table[,data$fraction =="fraction7"]
table.frxn8 <- NS_Table[,data$fraction =="fraction8"]
table.frxn9 <- NS_Table[,data$fraction =="fraction9"]
table.frxn10 <- NS_Table[,data$fraction =="fraction10"]
table.frxn11 <- NS_Table[,data$fraction =="fraction11"]
table.frxn12 <- NS_Table[,data$fraction =="fraction12"]
table.frxn13 <- NS_Table[,data$fraction =="fraction13"]
table.frxn14 <- NS_Table[,data$fraction =="fraction14"]
table.frxn15 <- NS_Table[,data$fraction =="fraction15"]
table.frxn16 <- NS_Table[,data$fraction =="fraction16"]
table.frxn17 <- NS_Table[,data$fraction =="fraction17"]
table.frxn18 <- NS_Table[,data$fraction =="fraction18"]
table.frxn19 <- NS_Table[,data$fraction =="fraction19"]
table.frxn20 <- NS_Table[,data$fraction =="fraction20"]
table.frxn21 <- NS_Table[,data$fraction =="fraction21"]
table.frxn22 <- NS_Table[,data$fraction =="fraction22"]
table.frxn23 <- NS_Table[,data$fraction =="fraction23"]
table.frxn24 <- NS_Table[,data$fraction =="fraction24"]
table.frxn25 <- NS_Table[,data$fraction =="fraction25"]

```

```{r}
# Re-define the information for the fraction subtables (dataframe named "data3") and create one table per treatment and per fraction. Here there are 50 subtables in total
# A new table is defined for each fraction, containing 3 replicates of either CTRL or RNASE.

# CODE: data3 serves as an auxiliary table used to more easily select the correct columns of CTRL or RNASE replicates for the new tables.
data3 <- data.frame(row.names=colnames(table.frxn1), treatment = rep(c("CTRL", "RNASE"),3), condition = c("ctrl1","rnase1","ctrl2","rnase2","ctrl3","rnase3"))

table.frxn1.CTRL <- table.frxn1[,data3$treatment == "CTRL"] 
table.frxn1.RNASE <- table.frxn1[,data3$treatment == "RNASE"]
table.frxn2.CTRL <- table.frxn2[,data3$treatment == "CTRL"] 
table.frxn2.RNASE <- table.frxn2[,data3$treatment == "RNASE"]
table.frxn3.CTRL <- table.frxn3[,data3$treatment == "CTRL"] 
table.frxn3.RNASE <- table.frxn3[,data3$treatment == "RNASE"]
table.frxn4.CTRL <- table.frxn4[,data3$treatment == "CTRL"] 
table.frxn4.RNASE <- table.frxn4[,data3$treatment == "RNASE"]
table.frxn5.CTRL <- table.frxn5[,data3$treatment == "CTRL"] 
table.frxn5.RNASE <- table.frxn5[,data3$treatment == "RNASE"]
table.frxn6.CTRL <- table.frxn6[,data3$treatment == "CTRL"] 
table.frxn6.RNASE <- table.frxn6[,data3$treatment == "RNASE"]
table.frxn7.CTRL <- table.frxn7[,data3$treatment == "CTRL"] 
table.frxn7.RNASE <- table.frxn7[,data3$treatment == "RNASE"]
table.frxn8.CTRL <- table.frxn8[,data3$treatment == "CTRL"] 
table.frxn8.RNASE <- table.frxn8[,data3$treatment == "RNASE"]
table.frxn9.CTRL <- table.frxn9[,data3$treatment == "CTRL"] 
table.frxn9.RNASE <- table.frxn9[,data3$treatment == "RNASE"]
table.frxn10.CTRL <- table.frxn10[,data3$treatment == "CTRL"] 
table.frxn10.RNASE <- table.frxn10[,data3$treatment == "RNASE"]
table.frxn11.CTRL <- table.frxn11[,data3$treatment == "CTRL"] 
table.frxn11.RNASE <- table.frxn11[,data3$treatment == "RNASE"]
table.frxn12.CTRL <- table.frxn12[,data3$treatment == "CTRL"] 
table.frxn12.RNASE <- table.frxn12[,data3$treatment == "RNASE"]
table.frxn13.CTRL <- table.frxn13[,data3$treatment == "CTRL"] 
table.frxn13.RNASE <- table.frxn13[,data3$treatment == "RNASE"]
table.frxn14.CTRL <- table.frxn14[,data3$treatment == "CTRL"] 
table.frxn14.RNASE <- table.frxn14[,data3$treatment == "RNASE"]
table.frxn15.CTRL <- table.frxn15[,data3$treatment == "CTRL"] 
table.frxn15.RNASE <- table.frxn15[,data3$treatment == "RNASE"]
table.frxn16.CTRL <- table.frxn16[,data3$treatment == "CTRL"] 
table.frxn16.RNASE <- table.frxn16[,data3$treatment == "RNASE"]
table.frxn17.CTRL <- table.frxn17[,data3$treatment == "CTRL"] 
table.frxn17.RNASE <- table.frxn17[,data3$treatment == "RNASE"]
table.frxn18.CTRL <- table.frxn18[,data3$treatment == "CTRL"] 
table.frxn18.RNASE <- table.frxn18[,data3$treatment == "RNASE"]
table.frxn19.CTRL <- table.frxn19[,data3$treatment == "CTRL"] 
table.frxn19.RNASE <- table.frxn19[,data3$treatment == "RNASE"]
table.frxn20.CTRL <- table.frxn20[,data3$treatment == "CTRL"] 
table.frxn20.RNASE <- table.frxn20[,data3$treatment == "RNASE"]
table.frxn21.CTRL <- table.frxn21[,data3$treatment == "CTRL"] 
table.frxn21.RNASE <- table.frxn21[,data3$treatment == "RNASE"]
table.frxn22.CTRL <- table.frxn22[,data3$treatment == "CTRL"] 
table.frxn22.RNASE <- table.frxn22[,data3$treatment == "RNASE"]
table.frxn23.CTRL <- table.frxn23[,data3$treatment == "CTRL"] 
table.frxn23.RNASE <- table.frxn23[,data3$treatment == "RNASE"]
table.frxn24.CTRL <- table.frxn24[,data3$treatment == "CTRL"] 
table.frxn24.RNASE <- table.frxn24[,data3$treatment == "RNASE"]
table.frxn25.CTRL <- table.frxn25[,data3$treatment == "CTRL"] 
table.frxn25.RNASE <- table.frxn25[,data3$treatment == "RNASE"]

```


```{r}
# Determine average values for each treatment, each fraction and each replicate. Here, the values for the three replicates are stored in the same table
# Each vector contains the average protein value across all proteins for each of its 3 replicates.
avg.table.frxn1.CTRL <- sapply(table.frxn1.CTRL, function(x) mean(x))
avg.table.frxn2.CTRL <- sapply(table.frxn2.CTRL, function(x) mean(x))
avg.table.frxn3.CTRL <- sapply(table.frxn3.CTRL, function(x) mean(x))
avg.table.frxn4.CTRL <- sapply(table.frxn4.CTRL, function(x) mean(x))
avg.table.frxn5.CTRL <- sapply(table.frxn5.CTRL, function(x) mean(x))
avg.table.frxn6.CTRL <- sapply(table.frxn6.CTRL, function(x) mean(x))
avg.table.frxn7.CTRL <- sapply(table.frxn7.CTRL, function(x) mean(x))
avg.table.frxn8.CTRL <- sapply(table.frxn8.CTRL, function(x) mean(x))
avg.table.frxn9.CTRL <- sapply(table.frxn9.CTRL, function(x) mean(x))
avg.table.frxn10.CTRL <- sapply(table.frxn10.CTRL, function(x) mean(x))
avg.table.frxn11.CTRL <- sapply(table.frxn11.CTRL, function(x) mean(x))
avg.table.frxn12.CTRL <- sapply(table.frxn12.CTRL, function(x) mean(x))
avg.table.frxn13.CTRL <- sapply(table.frxn13.CTRL, function(x) mean(x))
avg.table.frxn14.CTRL <- sapply(table.frxn14.CTRL, function(x) mean(x))
avg.table.frxn15.CTRL <- sapply(table.frxn15.CTRL, function(x) mean(x))
avg.table.frxn16.CTRL <- sapply(table.frxn16.CTRL, function(x) mean(x))
avg.table.frxn17.CTRL <- sapply(table.frxn17.CTRL, function(x) mean(x))
avg.table.frxn18.CTRL <- sapply(table.frxn18.CTRL, function(x) mean(x))
avg.table.frxn19.CTRL <- sapply(table.frxn19.CTRL, function(x) mean(x))
avg.table.frxn20.CTRL <- sapply(table.frxn20.CTRL, function(x) mean(x))
avg.table.frxn21.CTRL <- sapply(table.frxn21.CTRL, function(x) mean(x))
avg.table.frxn22.CTRL <- sapply(table.frxn22.CTRL, function(x) mean(x))
avg.table.frxn23.CTRL <- sapply(table.frxn23.CTRL, function(x) mean(x))
avg.table.frxn24.CTRL <- sapply(table.frxn24.CTRL, function(x) mean(x))
avg.table.frxn25.CTRL <- sapply(table.frxn25.CTRL, function(x) mean(x))

avg.table.frxn1.RNASE <- sapply(table.frxn1.RNASE, function(x) mean(x))
avg.table.frxn2.RNASE <- sapply(table.frxn2.RNASE, function(x) mean(x))
avg.table.frxn3.RNASE <- sapply(table.frxn3.RNASE, function(x) mean(x))
avg.table.frxn4.RNASE <- sapply(table.frxn4.RNASE, function(x) mean(x))
avg.table.frxn5.RNASE <- sapply(table.frxn5.RNASE, function(x) mean(x))
avg.table.frxn6.RNASE <- sapply(table.frxn6.RNASE, function(x) mean(x))
avg.table.frxn7.RNASE <- sapply(table.frxn7.RNASE, function(x) mean(x))
avg.table.frxn8.RNASE <- sapply(table.frxn8.RNASE, function(x) mean(x))
avg.table.frxn9.RNASE <- sapply(table.frxn9.RNASE, function(x) mean(x))
avg.table.frxn10.RNASE <- sapply(table.frxn10.RNASE, function(x) mean(x))
avg.table.frxn11.RNASE <- sapply(table.frxn11.RNASE, function(x) mean(x))
avg.table.frxn12.RNASE <- sapply(table.frxn12.RNASE, function(x) mean(x))
avg.table.frxn13.RNASE <- sapply(table.frxn13.RNASE, function(x) mean(x))
avg.table.frxn14.RNASE <- sapply(table.frxn14.RNASE, function(x) mean(x))
avg.table.frxn15.RNASE <- sapply(table.frxn15.RNASE, function(x) mean(x))
avg.table.frxn16.RNASE <- sapply(table.frxn16.RNASE, function(x) mean(x))
avg.table.frxn17.RNASE <- sapply(table.frxn17.RNASE, function(x) mean(x))
avg.table.frxn18.RNASE <- sapply(table.frxn18.RNASE, function(x) mean(x))
avg.table.frxn19.RNASE <- sapply(table.frxn19.RNASE, function(x) mean(x))
avg.table.frxn20.RNASE <- sapply(table.frxn20.RNASE, function(x) mean(x))
avg.table.frxn21.RNASE <- sapply(table.frxn21.RNASE, function(x) mean(x))
avg.table.frxn22.RNASE <- sapply(table.frxn22.RNASE, function(x) mean(x))
avg.table.frxn23.RNASE <- sapply(table.frxn23.RNASE, function(x) mean(x))
avg.table.frxn24.RNASE <- sapply(table.frxn24.RNASE, function(x) mean(x))
avg.table.frxn25.RNASE <- sapply(table.frxn25.RNASE, function(x) mean(x))
```

++++++++++++++++++
FEHLER nach Z.235: Warnung: Argument ist weder numerisch noch boolesch: gebe NA
Idee: table.frxn1.CTRL <- as.numeric(table.frxn1.CTRL)
Fehler: 'list' Objekt kann nicht in Typ 'double' umgewandelt werden
->Wie lösen?
++++++++++++++++++

```{r}
# Determine normalization factor for each condition, as the mean of the 2 most similar replicates
# Create a function norm_fact for this step:
norm_fact <- function(x) {
				if( (abs(x[1]-x[2])<abs(x[1]-x[3])) && (abs(x[1]-x[2])<abs(x[2]-x[3])) ) 
					{mean(c(x[1],x[2]))} else if( (abs(x[1]-x[3])<abs(x[1]-x[2])) && (abs(x[1]-x[3])<abs(x[2]-x[3])) )
												  {mean(c(x[1],x[3]))} else {mean(c(x[2],x[3]))} 
                        }
```

```{r}
# Determine the normalization factor for the CTRL fractions and for the RNASE fractions
norm_mean_frxn1_CTRL <-  norm_fact(avg.table.frxn1.CTRL)/avg.table.frxn1.CTRL
norm_mean_frxn2_CTRL <-  norm_fact(avg.table.frxn2.CTRL)/avg.table.frxn2.CTRL
norm_mean_frxn3_CTRL <-  norm_fact(avg.table.frxn3.CTRL)/avg.table.frxn3.CTRL
norm_mean_frxn4_CTRL <-  norm_fact(avg.table.frxn4.CTRL)/avg.table.frxn4.CTRL
norm_mean_frxn5_CTRL <-  norm_fact(avg.table.frxn5.CTRL)/avg.table.frxn5.CTRL
norm_mean_frxn6_CTRL <-  norm_fact(avg.table.frxn6.CTRL)/avg.table.frxn6.CTRL
norm_mean_frxn7_CTRL <-  norm_fact(avg.table.frxn7.CTRL)/avg.table.frxn7.CTRL
norm_mean_frxn8_CTRL <-  norm_fact(avg.table.frxn8.CTRL)/avg.table.frxn8.CTRL
norm_mean_frxn9_CTRL <-  norm_fact(avg.table.frxn9.CTRL)/avg.table.frxn9.CTRL
norm_mean_frxn10_CTRL <-  norm_fact(avg.table.frxn10.CTRL)/avg.table.frxn10.CTRL
norm_mean_frxn11_CTRL <-  norm_fact(avg.table.frxn11.CTRL)/avg.table.frxn11.CTRL
norm_mean_frxn12_CTRL <-  norm_fact(avg.table.frxn12.CTRL)/avg.table.frxn12.CTRL
norm_mean_frxn13_CTRL <-  norm_fact(avg.table.frxn13.CTRL)/avg.table.frxn13.CTRL
norm_mean_frxn14_CTRL <-  norm_fact(avg.table.frxn14.CTRL)/avg.table.frxn14.CTRL
norm_mean_frxn15_CTRL <-  norm_fact(avg.table.frxn15.CTRL)/avg.table.frxn15.CTRL
norm_mean_frxn16_CTRL <-  norm_fact(avg.table.frxn16.CTRL)/avg.table.frxn16.CTRL
norm_mean_frxn17_CTRL <-  norm_fact(avg.table.frxn17.CTRL)/avg.table.frxn17.CTRL
norm_mean_frxn18_CTRL <-  norm_fact(avg.table.frxn18.CTRL)/avg.table.frxn18.CTRL
norm_mean_frxn19_CTRL <-  norm_fact(avg.table.frxn19.CTRL)/avg.table.frxn19.CTRL
norm_mean_frxn20_CTRL <-  norm_fact(avg.table.frxn20.CTRL)/avg.table.frxn20.CTRL
norm_mean_frxn21_CTRL <-  norm_fact(avg.table.frxn21.CTRL)/avg.table.frxn21.CTRL
norm_mean_frxn22_CTRL <-  norm_fact(avg.table.frxn22.CTRL)/avg.table.frxn22.CTRL
norm_mean_frxn23_CTRL <-  norm_fact(avg.table.frxn23.CTRL)/avg.table.frxn23.CTRL
norm_mean_frxn24_CTRL <-  norm_fact(avg.table.frxn24.CTRL)/avg.table.frxn24.CTRL
norm_mean_frxn25_CTRL <-  norm_fact(avg.table.frxn25.CTRL)/avg.table.frxn25.CTRL

norm_mean_frxn1_RNASE <-  norm_fact(avg.table.frxn1.RNASE)/avg.table.frxn1.RNASE
norm_mean_frxn2_RNASE <-  norm_fact(avg.table.frxn2.RNASE)/avg.table.frxn2.RNASE
norm_mean_frxn3_RNASE <-  norm_fact(avg.table.frxn3.RNASE)/avg.table.frxn3.RNASE
norm_mean_frxn4_RNASE <-  norm_fact(avg.table.frxn4.RNASE)/avg.table.frxn4.RNASE
norm_mean_frxn5_RNASE <-  norm_fact(avg.table.frxn5.RNASE)/avg.table.frxn5.RNASE
norm_mean_frxn6_RNASE <-  norm_fact(avg.table.frxn6.RNASE)/avg.table.frxn6.RNASE
norm_mean_frxn7_RNASE <-  norm_fact(avg.table.frxn7.RNASE)/avg.table.frxn7.RNASE
norm_mean_frxn8_RNASE <-  norm_fact(avg.table.frxn8.RNASE)/avg.table.frxn8.RNASE
norm_mean_frxn9_RNASE <-  norm_fact(avg.table.frxn9.RNASE)/avg.table.frxn9.RNASE
norm_mean_frxn10_RNASE <-  norm_fact(avg.table.frxn10.RNASE)/avg.table.frxn10.RNASE
norm_mean_frxn11_RNASE <-  norm_fact(avg.table.frxn11.RNASE)/avg.table.frxn11.RNASE
norm_mean_frxn12_RNASE <-  norm_fact(avg.table.frxn12.RNASE)/avg.table.frxn12.RNASE
norm_mean_frxn13_RNASE <-  norm_fact(avg.table.frxn13.RNASE)/avg.table.frxn13.RNASE
norm_mean_frxn14_RNASE <-  norm_fact(avg.table.frxn14.RNASE)/avg.table.frxn14.RNASE
norm_mean_frxn15_RNASE <-  norm_fact(avg.table.frxn15.RNASE)/avg.table.frxn15.RNASE
norm_mean_frxn16_RNASE <-  norm_fact(avg.table.frxn16.RNASE)/avg.table.frxn16.RNASE
norm_mean_frxn17_RNASE <-  norm_fact(avg.table.frxn17.RNASE)/avg.table.frxn17.RNASE
norm_mean_frxn18_RNASE <-  norm_fact(avg.table.frxn18.RNASE)/avg.table.frxn18.RNASE
norm_mean_frxn19_RNASE <-  norm_fact(avg.table.frxn19.RNASE)/avg.table.frxn19.RNASE
norm_mean_frxn20_RNASE <-  norm_fact(avg.table.frxn20.RNASE)/avg.table.frxn20.RNASE
norm_mean_frxn21_RNASE <-  norm_fact(avg.table.frxn21.RNASE)/avg.table.frxn21.RNASE
norm_mean_frxn22_RNASE <-  norm_fact(avg.table.frxn22.RNASE)/avg.table.frxn22.RNASE
norm_mean_frxn23_RNASE <-  norm_fact(avg.table.frxn23.RNASE)/avg.table.frxn23.RNASE
norm_mean_frxn24_RNASE <-  norm_fact(avg.table.frxn24.RNASE)/avg.table.frxn24.RNASE
norm_mean_frxn25_RNASE <-  norm_fact(avg.table.frxn25.RNASE)/avg.table.frxn25.RNASE

```
```{r}
# Compute vectors containing the normalization factors for the respective treatment and replicates and fractions 1 to 25
norm.ctrl1 <- c(norm_mean_frxn1_CTRL[1],norm_mean_frxn2_CTRL[1],norm_mean_frxn3_CTRL[1],norm_mean_frxn4_CTRL[1],norm_mean_frxn5_CTRL[1],norm_mean_frxn6_CTRL[1],norm_mean_frxn7_CTRL[1],norm_mean_frxn8_CTRL[1],norm_mean_frxn9_CTRL[1],norm_mean_frxn10_CTRL[1],norm_mean_frxn11_CTRL[1],norm_mean_frxn12_CTRL[1],norm_mean_frxn13_CTRL[1],norm_mean_frxn14_CTRL[1],norm_mean_frxn15_CTRL[1],norm_mean_frxn16_CTRL[1],norm_mean_frxn17_CTRL[1],norm_mean_frxn18_CTRL[1],norm_mean_frxn19_CTRL[1],norm_mean_frxn20_CTRL[1],norm_mean_frxn21_CTRL[1],norm_mean_frxn22_CTRL[1],norm_mean_frxn23_CTRL[1],norm_mean_frxn24_CTRL[1],norm_mean_frxn25_CTRL[1])
norm.ctrl2 <- c(norm_mean_frxn1_CTRL[2],norm_mean_frxn2_CTRL[2],norm_mean_frxn3_CTRL[2],norm_mean_frxn4_CTRL[2],norm_mean_frxn5_CTRL[2],norm_mean_frxn6_CTRL[2],norm_mean_frxn7_CTRL[2],norm_mean_frxn8_CTRL[2],norm_mean_frxn9_CTRL[2],norm_mean_frxn10_CTRL[2],norm_mean_frxn11_CTRL[2],norm_mean_frxn12_CTRL[2],norm_mean_frxn13_CTRL[2],norm_mean_frxn14_CTRL[2],norm_mean_frxn15_CTRL[2],norm_mean_frxn16_CTRL[2],norm_mean_frxn17_CTRL[2],norm_mean_frxn18_CTRL[2],norm_mean_frxn19_CTRL[2],norm_mean_frxn20_CTRL[2],norm_mean_frxn21_CTRL[2],norm_mean_frxn22_CTRL[2],norm_mean_frxn23_CTRL[2],norm_mean_frxn24_CTRL[2],norm_mean_frxn25_CTRL[2])
norm.ctrl3 <- c(norm_mean_frxn1_CTRL[3],norm_mean_frxn2_CTRL[3],norm_mean_frxn3_CTRL[3],norm_mean_frxn4_CTRL[3],norm_mean_frxn5_CTRL[3],norm_mean_frxn6_CTRL[3],norm_mean_frxn7_CTRL[3],norm_mean_frxn8_CTRL[3],norm_mean_frxn9_CTRL[3],norm_mean_frxn10_CTRL[3],norm_mean_frxn11_CTRL[3],norm_mean_frxn12_CTRL[3],norm_mean_frxn13_CTRL[3],norm_mean_frxn14_CTRL[3],norm_mean_frxn15_CTRL[3],norm_mean_frxn16_CTRL[3],norm_mean_frxn17_CTRL[3],norm_mean_frxn18_CTRL[3],norm_mean_frxn19_CTRL[3],norm_mean_frxn20_CTRL[3],norm_mean_frxn21_CTRL[3],norm_mean_frxn22_CTRL[3],norm_mean_frxn23_CTRL[3],norm_mean_frxn24_CTRL[3],norm_mean_frxn25_CTRL[3])

norm.rnase1 <- c(norm_mean_frxn1_RNASE[1],norm_mean_frxn2_RNASE[1],norm_mean_frxn3_RNASE[1],norm_mean_frxn4_RNASE[1],norm_mean_frxn5_RNASE[1],norm_mean_frxn6_RNASE[1],norm_mean_frxn7_RNASE[1],norm_mean_frxn8_RNASE[1],norm_mean_frxn9_RNASE[1],norm_mean_frxn10_RNASE[1],norm_mean_frxn11_RNASE[1],norm_mean_frxn12_RNASE[1],norm_mean_frxn13_RNASE[1],norm_mean_frxn14_RNASE[1],norm_mean_frxn15_RNASE[1],norm_mean_frxn16_RNASE[1],norm_mean_frxn17_RNASE[1],norm_mean_frxn18_RNASE[1],norm_mean_frxn19_RNASE[1],norm_mean_frxn20_RNASE[1],norm_mean_frxn21_RNASE[1],norm_mean_frxn22_RNASE[1],norm_mean_frxn23_RNASE[1],norm_mean_frxn24_RNASE[1],norm_mean_frxn25_RNASE[1])
norm.rnase2 <- c(norm_mean_frxn1_RNASE[2],norm_mean_frxn2_RNASE[2],norm_mean_frxn3_RNASE[2],norm_mean_frxn4_RNASE[2],norm_mean_frxn5_RNASE[2],norm_mean_frxn6_RNASE[2],norm_mean_frxn7_RNASE[2],norm_mean_frxn8_RNASE[2],norm_mean_frxn9_RNASE[2],norm_mean_frxn10_RNASE[2],norm_mean_frxn11_RNASE[2],norm_mean_frxn12_RNASE[2],norm_mean_frxn13_RNASE[2],norm_mean_frxn14_RNASE[2],norm_mean_frxn15_RNASE[2],norm_mean_frxn16_RNASE[2],norm_mean_frxn17_RNASE[2],norm_mean_frxn18_RNASE[2],norm_mean_frxn19_RNASE[2],norm_mean_frxn20_RNASE[2],norm_mean_frxn21_RNASE[2],norm_mean_frxn22_RNASE[2],norm_mean_frxn23_RNASE[2],norm_mean_frxn24_RNASE[2],norm_mean_frxn25_RNASE[2])
norm.rnase3 <- c(norm_mean_frxn1_RNASE[3],norm_mean_frxn2_RNASE[3],norm_mean_frxn3_RNASE[3],norm_mean_frxn4_RNASE[3],norm_mean_frxn5_RNASE[3],norm_mean_frxn6_RNASE[3],norm_mean_frxn7_RNASE[3],norm_mean_frxn8_RNASE[3],norm_mean_frxn9_RNASE[3],norm_mean_frxn10_RNASE[3],norm_mean_frxn11_RNASE[3],norm_mean_frxn12_RNASE[3],norm_mean_frxn13_RNASE[3],norm_mean_frxn14_RNASE[3],norm_mean_frxn15_RNASE[3],norm_mean_frxn16_RNASE[3],norm_mean_frxn17_RNASE[3],norm_mean_frxn18_RNASE[3],norm_mean_frxn19_RNASE[3],norm_mean_frxn20_RNASE[3],norm_mean_frxn21_RNASE[3],norm_mean_frxn22_RNASE[3],norm_mean_frxn23_RNASE[3],norm_mean_frxn24_RNASE[3],norm_mean_frxn25_RNASE[3])

```

```{r}
# Define subtables for each treatment and each replicate 
data.ctrl1 <- data$condition =="ctrl1"
data.ctrl2 <- data$condition =="ctrl2"
data.ctrl3 <- data$condition =="ctrl3"
data.rnase1 <- data$condition =="rnase1"
data.rnase2 <- data$condition =="rnase2"
data.rnase3 <- data$condition =="rnase3"

```

**************************************************************************************************************
```{r}
# Normalization step, fraction-wise
table.ctrl1 <- data.frame(mapply('*', table[,data.ctrl1], norm.ctrl1, SIMPLIFY=FALSE))
table.ctrl2 <- data.frame(mapply('*', table[,data.ctrl2], norm.ctrl2, SIMPLIFY=FALSE))
table.ctrl3 <- data.frame(mapply('*', table[,data.ctrl3], norm.ctrl3, SIMPLIFY=FALSE))

table.rnase1 <- data.frame(mapply('*', table[,data.rnase1], norm.rnase1, SIMPLIFY=FALSE))
table.rnase2 <- data.frame(mapply('*', table[,data.rnase2], norm.rnase2, SIMPLIFY=FALSE))
table.rnase3 <- data.frame(mapply('*', table[,data.rnase3], norm.rnase3, SIMPLIFY=FALSE))

```

```{r}
# Get the proper rownames for the tables
rownames(table.ctrl1) <- row_names
rownames(table.ctrl2) <- row_names
rownames(table.ctrl3) <- row_names
rownames(table.rnase1) <- row_names
rownames(table.rnase2) <- row_names
rownames(table.rnase3) <- row_names
```

**************************************************************************************************************
```{r}
#### Apply a sliding window/moving average of 3 points to the data ####
table.ctrl1.SW <- data.frame(table.ctrl1[1],(table.ctrl1[1:23]+table.ctrl1[2:24]+table.ctrl1[3:25])/3,table.ctrl1[25])
table.ctrl2.SW <- data.frame(table.ctrl2[1],(table.ctrl2[1:23]+table.ctrl2[2:24]+table.ctrl2[3:25])/3,table.ctrl2[25])
table.ctrl3.SW <- data.frame(table.ctrl3[1],(table.ctrl3[1:23]+table.ctrl3[2:24]+table.ctrl3[3:25])/3,table.ctrl3[25])
table.rnase1.SW <- data.frame(table.rnase1[1],(table.rnase1[1:23]+table.rnase1[2:24]+table.rnase1[3:25])/3,table.rnase1[25])
table.rnase2.SW <- data.frame(table.rnase2[1],(table.rnase2[1:23]+table.rnase2[2:24]+table.rnase2[3:25])/3,table.rnase2[25])
table.rnase3.SW <- data.frame(table.rnase3[1],(table.rnase3[1:23]+table.rnase3[2:24]+table.rnase3[3:25])/3,table.rnase3[25])

```

```{r}
# Get the proper rownames for the tables
colnames(table.ctrl1.SW) <- colnames(table.ctrl1)
colnames(table.ctrl2.SW) <- colnames(table.ctrl2)
colnames(table.ctrl3.SW) <- colnames(table.ctrl3)
colnames(table.rnase1.SW) <- colnames(table.rnase1)
colnames(table.rnase2.SW) <- colnames(table.rnase2)
colnames(table.rnase3.SW) <- colnames(table.rnase3)
```

**************************************************************************************************************
```{r}
#### Normaliztion over the amount to sum = 100 (%) ####

table.ctrl1.SW.norm <- table.ctrl1.SW * 100 / rowSums(table.ctrl1.SW)
table.ctrl2.SW.norm <- table.ctrl2.SW * 100 / rowSums(table.ctrl2.SW)
table.ctrl3.SW.norm <- table.ctrl3.SW * 100 / rowSums(table.ctrl3.SW)

table.rnase1.SW.norm <- table.rnase1.SW * 100 / rowSums(table.rnase1.SW)
table.rnase2.SW.norm <- table.rnase2.SW * 100 / rowSums(table.rnase2.SW)
table.rnase3.SW.norm <- table.rnase3.SW * 100 / rowSums(table.rnase3.SW)
```

**************************************************************************************************************
```{r}
# Replace NA, NaN with 0 if any
table.ctrl1.SW.norm <- rapply(table.ctrl1.SW.norm, f=function(x) ifelse(is.na(x),0,x), how="replace") 
table.ctrl2.SW.norm <- rapply(table.ctrl2.SW.norm, f=function(x) ifelse(is.na(x),0,x), how="replace" )
table.ctrl3.SW.norm <- rapply(table.ctrl3.SW.norm, f=function(x) ifelse(is.na(x),0,x), how="replace" )
table.rnase1.SW.norm <- rapply(table.rnase1.SW.norm, f=function(x) ifelse(is.na(x),0,x), how="replace" )
table.rnase2.SW.norm <- rapply(table.rnase2.SW.norm, f=function(x) ifelse(is.na(x),0,x), how="replace" )
table.rnase3.SW.norm <- rapply(table.rnase3.SW.norm, f=function(x) ifelse(is.na(x),0,x), how="replace" )

table.ctrl1.SW.norm <- rapply(table.ctrl1.SW.norm, f=function(x) ifelse(is.nan(x),0,x), how="replace") 
table.ctrl2.SW.norm <- rapply(table.ctrl2.SW.norm, f=function(x) ifelse(is.nan(x),0,x), how="replace" )
table.ctrl3.SW.norm <- rapply(table.ctrl3.SW.norm, f=function(x) ifelse(is.nan(x),0,x), how="replace" )
table.rnase1.SW.norm <- rapply(table.rnase1.SW.norm, f=function(x) ifelse(is.nan(x),0,x), how="replace" )
table.rnase2.SW.norm <- rapply(table.rnase2.SW.norm, f=function(x) ifelse(is.nan(x),0,x), how="replace" )
table.rnase3.SW.norm <- rapply(table.rnase3.SW.norm, f=function(x) ifelse(is.nan(x),0,x), how="replace" )

```

**************************************************************************************************************
```{r}
# Average value for normalization of CTRL and RNASE samples to 100
my.list.ctrl.norm <- list(table.ctrl1.SW, table.ctrl2.SW, table.ctrl3.SW)
my.list.rnase.norm <- list(table.rnase1.SW, table.rnase2.SW, table.rnase3.SW)

ctrl_norm_mean <- Reduce("+", my.list.ctrl.norm)/length(my.list.ctrl.norm)
rnase_norm_mean <- Reduce("+", my.list.rnase.norm)/length(my.list.rnase.norm)
```

```{r}
# Change names of the columns: from "fraction1" to "fraction25"
col_fractions <- paste("fraction",1:25,sep="")
colnames(ctrl_norm_mean) <- col_fractions
colnames(rnase_norm_mean) <- col_fractions
```

```{r}
# Normalization to 100 for each protein (= the sum of the amount of protein from fraction1 to fraction25 is 100)
ctrl_norm_mean <- ctrl_norm_mean*100/rowSums(ctrl_norm_mean)
rnase_norm_mean <- rnase_norm_mean*100/rowSums(rnase_norm_mean)

```

```{r}
# Replace the NaN and NA values by 0 if any
ctrl_norm_mean <- rapply(ctrl_norm_mean, f=function(x) ifelse(is.nan(x),0,x), how="replace")
rnase_norm_mean <- rapply(rnase_norm_mean, f=function(x) ifelse(is.nan(x),0,x), how="replace")
ctrl_norm_mean <- rapply(ctrl_norm_mean, f=function(x) ifelse(is.na(x),0,x), how="replace")
rnase_norm_mean <- rapply(rnase_norm_mean, f=function(x) ifelse(is.na(x),0,x), how="replace")

```

```{r}
# If one of the curve is 0 over all the fractions of one condition, the other condition will be set to 0 to take it out of the analysis
ctrl_norm_mean[rowSums(rnase_norm_mean[1:25])==0,] <- 0
rnase_norm_mean[rowSums(ctrl_norm_mean[1:25])==0,] <- 0

```

**************************************************************************************************************
2 - Find local maxima greater than 2 as fit parameters
**************************************************************************************************************

**************************************************************************************************************
```{r}
#General first overview of data

# Dimension
dim(NS_Table)
# Number of columns
ncol(NS_Table)
# Number of rows
nrow(NS_Table)

colnames(NS_Table)
rownames(NS_Table)
head(NS_Table)
summary(NS_Table)
```

```{r}
#Check for missing values
anyNA(NS_Table)
```

